Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-03-01 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: organizing a bit

We now turn our attention to dCS gravity.
%
In Fig.~\ref{fig:dCS_exec_sum} we show the marginalized posterior distribution
function of $\ell_{\rm CS}$ for both events GW150914 (top panel) and GW200129
(middle panel), with (dashed line) and without (solid line) spin corrections to
dominant $l = m = 2$,~$n=0$~QNM.
%
Perhaps the most salient feature of these posteriors is that they are not
peaked at $\ell_{\rm CS}$, which may mislead us to believe that we are seeing a
deviation from GR. This is not the case. We must remember that in the {\sc
Parspec} formalism the GR deviations are controlled by $\gamma \, \delta
\omega^{(j)}$~and~$\gamma \, \delta \tau^{(j)}$, and these, indeed, do peak at
zero. (See Fig. xx discussed below.)
%
We also see that in both cases, that the inclusion leading-order-in-spin
correction to the mode, displaces the posteriors towards smaller values of
$\ell_{\rm CS}$. This can be seen more evidently by looking at the location of
posterior peaks.
%
Finally, in the bottom panel, we show the combined result for both events.

@@

We also found for both GW events, that the
perturbative-conditions~\ref{eq:parspec_bound} imposed by the {\sc Parspec}
formalism are violated for the $\gamma_{\rm CS} \delta \tau^{(1)}$ coefficient.
%
This means that we cannot use these posterior to infer any meaningful bound on dCS gravity.
%
Now, since both event individually led to a bound on $\ell_{\rm CS}$ (assuming a cut-off scale for $\gm = M_{f}$
and $j = 0$), we can combine the posteriors to obtain the cumulative bound,
%
\begin{equation}
\ell_{\rm CS} \leqslant 34.5~\textrm{km}
\quad \textrm{(90\% credibility)},
\end{equation}
%
which is the main result of this section.
%
This bound is approximately a factor of four weaker than that placed by
Ref.~\cite{Silva:2020acr}, but
%
(i) relies only on GW observations and
%
(ii) suggests that a ringdown analysis can potentially place constraints on
theories which evade GW tests using inspiral information alone, such as the
case of dCS gravity~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
%
In Table~\ref{tab:summary_dcs} we summarize our findings of this section.

>>>>

We now turn our attention to dCS gravity.
%
In Fig.~\ref{fig:dCS_exec_sum} we show the marginalized posterior distribution
function of $\ell_{\rm CS}$ for both events GW150914 (top panel) and GW200129
(middle panel), with (dashed line) and without (solid line) spin corrections to
dominant $l = m = 2$,~$n=0$~QNM.
%
Perhaps the most salient feature of these posteriors is that they are not
peaked at $\ell_{\rm CS}$, which may mislead us to believe that we are seeing a
deviation from GR. This is not the case.
%
We must remember that in the {\sc Parspec} formalism that the GR deviations
are controlled by $\gamma \, \delta \omega^{(j)}$~and~$\gamma \, \delta \tau^{(j)}$.
We verified that these quantities do indeed peak at zero indicating consistency with GR.
%
We also see that in both cases, that the inclusion leading-order-in-spin
correction to the mode, displaces the posteriors towards smaller values of
$\ell_{\rm CS}$. This can be seen more evidently by looking at the location of
posterior peaks.
%
Finally, in the bottom panel, we show the combined result for both events.

@@

We also found for both GW events, that the
perturbative-conditions~\eqref{eq:parspec_bound} required by the {\sc Parspec}
formalism is violated for the $\gamma_{\rm CS} \delta \tau^{(1)}$ coefficient.
%
This means that we cannot use these posterior to infer any meaningful bound on dCS gravity
and that is why we quoted only the $j=0$ bound above.

Finally, since both event individually led to a bound on $\ell_{\rm CS}$
(assuming a cut-off scale for $\gm = M_{f}$ and $j = 0$), we can combine the
posteriors to obtain the cumulative bound,
%
\begin{equation}
\ell_{\rm CS} \leqslant 34.5~\textrm{km}
\quad \textrm{(90\% credibility)},
\end{equation}
%
which is the main result of this section.
%
This bound is approximately a factor of four weaker than that placed by
Ref.~\cite{Silva:2020acr}, but
%
(i) relies only on GW observations and
%
(ii) suggests that a ringdown analysis can potentially place constraints on
theories which evade GW tests using inspiral information alone, such as the
case of dCS gravity~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
%
In Table~\ref{tab:summary_dcs} we summarize our findings of this section.
